Modelling the gas kinematics of an atypical Lyman alpha emitting compact dwarf galaxy

### 2017-06-25 paper/paper.tex
discussion

\begin{abstract}
  Star-forming Compact Dwarf Galaxies (CDGs) resemble the expected
  pristine conditions of the first galaxies in the Universe and
  are the best systems to test models on primordial
galaxy formation and evolution.    
Here we report on one of such CDGs, \tol, which presents
a broad, single peaked, highly symmetric \lya\ line emission that had
evaded theoretical interpretation so far.  
In this paper we explain these features by two different physically
motivated kinematic models: 
an interstellar medium composed by outflowing clumps with 
random motions and an homogeneous gaseous sphere undergoing solid body
rotation.
It is the first time that an observed \lya\ spectrum can be explained
assuming either of these kinematic conditions.
We find that both models independently require high velocities, either
a clump velocity dispersion of \sigmaclump\ with outflows of
\inftyclump\ or a bulk rotation of $348^{+75}_{-48}$ km s$^{-1}$. 
The velocity dispersion in the multiphase model is consistent with a dynamical
mass of $2\times 10^{9}$ M$_{\odot}$, ten times its baryonic mass,
which can be explained if \tol\ is hosted by a dark matter halo of at least
$10^{11}$ M$_{\odot}$; cconditions similar to those of Dwarf Elliptical Galaxies.
This work shows the importance of considering multiphase
and rotation kinematics among the possible conditions shaping the
\lya\ spectra.
If future kinematic maps of \tol\ confirm the velocities found by the
multiphase model, it will be the basis to study new processes that
might be at play during primordial galaxy evolution.
\end{abstract}

@@

With $14$ free parameters our first concern is discovering which are
the most relevant in reproducing \tol's line shape.
The results of the random forest classifier yield that the clump outflow velocity
$v_{\infty,\rm{cl}}$, the clump velocity dispersion $\sigma_{\rm cl}$ and the probability
that the \lya\ emission comes from the clumps $P_{\rm cl}$ are the
most influential parameters in finding a model with low
$\chi^2/d.o.f.$.

Figure \ref{fig:tree} shows as an illustriation the results for one of such tree. 
Starting with $28$ and $1962$ models in the low and high
$\chi^2/d.o.f.$ classes respectively, we find that the best separation
yields $13$ and $44$ models after selecting for $v_{\infty,{\rm cl}}<157.0$ \kms,
$\sigma_{{\rm cl}}>55.6$ \kms and $P_{\rm cl}>0.683$.
The split is not perfect. This means that the three parameters in the
model are the most influential, but that some combinations of the
other 11 parameters are also relevant to find a good fit.

From the K-S tests we confirm that the same three parameters are the
only ones that can be constrained by observations;
$v_{\infty,\rm{cl}}$ (p-value  $10^{-18}$), $\sigma_{\rm cl}$ (p-value
$10^{-4}$) $P_{\rm cl}$ (p-value $10^{-4}$).
Once again, this test does not mean the other parameters do not
influence the resulting spectra at all; it means that they cannot be
constrained from \tol's observations.

@@

As a test, we ran a small set of 100 additional Monte-Carlo simulations
with random values for all parameters, except for $\sigma_{\rm cl}$,
$v_{\infty {\rm cl}}$, $P_{\rm cl}$ which where within the derived
constraints.
Consistent with the results from the random forest algorithm,
illustrated by the classification tree of Figure \ref{fig:tree}, we
found that $30$ models showed $\chi^2/d.o.f.<35$ values

@@

Having constrained only 3 parameters, one migh wonder why the other 11
parameters do not seem to matter. 
However, this view is misleading. 
Event if for clumply models the line profile is most sensitive to only
a few parameters \citep{Gronke2016}, there are the rest of parameters
which affect the line profile at a level that cannot be neglected,
i.e. we cannot randomly pick 11 random, reasonable values for these
parameters, and expect to fit the line profile while only varying the
other 3, as the results for the classification tree example show in
Figure \ref{fig:tree}.

@@

\tol\ shows one of the most atypical \lya\ spectra observed so far.
Its flux at the line's center is high compared to other LAEs at low
redshift and the broad, highly symmetrical peak is virtually absent from other
LAEs at low and high redshift
\citep{2012ApJ...751...29Y,LARS,Erb14,Trainor16}. 
Simple shell models
fail to reproduce such a spectrum as reported by \cite{2015A&A...578A...7V}.  
In the previous sections we show how these characteristics can be
explained by two different kinematic models. Which model should we prefer?

\tol's structural properties seem to be similar to observed dwarf
elliptical galaxies. 
The sample of 7 dwarf ellipticals (dE) observed by
\cite{2003AJ....126.1794G} show similar properties as \tol. 
For instance, the dE IC 3344 and IC 794 have similar absolute $M_V$
magnitudes (-17.10 and -17.19) and sizes (0.90 kpc and 0.82 kpc) than
\tol. These galaxies have velocity dispersions of $31.1$ \kms and
$44.6$ \kms, respectively,  and their rotational velocities are lower
than $1$ \kms.  
This coincidence leads us to prefer the multiphase model as it
provides at least some consistency with kinematic properties of other
dwarf elliptical galaxies.

Following the results of \cite{2011ApJ...726..108T}, who made a
detailed analysis for dwarf ellipticals, we can estimate a
value or the dynamical mass within $r$ using the constraints for the
velocity dispersion $\sigma$  in a spherical system localized in a
region of size $r$

\begin{equation}
M_{\rm dyn} = 3 \frac{\sigma ^{2}r}{G} = 3.48\times10^{9}
\left(\frac{\sigma}{100\ \mathrm{km\ s}^{-1}}\right)^2\left(\frac{r}{\mathrm{kpc}}\right)
M_{\odot}, 
\end{equation}
%
Assuming that the \lya\ emission is entirely powered by star formation 
we use the 3D half-light radius $r_s=2.25$ kpc as the typical size
for the HI region, in the multiphase model the clump velocity dispersion
$\sigma_{\rm{cl}}=$\sigmaclump corresponds to a dynamical mass of
$M_{\rm dyn}=2.31\pm0.04 \times 10^{9}$ $M_{\odot}$.

\cite{2011ApJ...726..108T} showed that  that such dynamical
mass can be explained if \tol\ is hosted by a dark matter halo of at
least $10^{11}$ M$_{\odot}$ in mass. 
This estimate is based on computing the integrated mass profile of a
spherical dark matter halo with a Navarro-Frenk-White profile with its
concentration following the \emph{median} mass-concentration
relationship found in the Bolshoi simulation
\citep{2012MNRAS.423.3018P}.

These results would imply that \tol\ is part of the dwarf ellipticals
class. However, there are two puzzles that are opened up by this. 
First, dwarf ellipticals are found either in clusters or groups of galaxies; while
\tol\ does not belong either to a group or a cluster
\citep{2001AJ....121..169F,}. 
The second problem is that, unlike dwarf
ellipticals, \tol\ hosts bright an compact startburst; imaging and
spectroscopy studies suggest that the startburst started less than 4
Myr ago, while the low surface brightness regins are consistent with
an age below one Gyr \citep{2001AJ....121..169F}.

@@

It is the first time that an observed \lya\ profile can be fully
reproduced by either of these two kinematic conditions.
The structural conditions in \tol\ are similar to those in dwarf
ellipticals. 
However, it environment and star forming activity are radically
different.
We suggest that additional integral field unit observations are the
only way to be certain about the detailed kinematic structure in \tol.

@@

We acknowledge that a final confirmation of our kinematic findings has
to be provided by new observational tests of the kind we suggest.
If that were the case, this would open up a new line of more detailed
enquiries to understand how a compact dwarf galaxy can have the
structural characteristics similar to a dwarf elliptical while being
at the same time isolated and sustaining large starburst.
If an evolutionary link is stablished between a phase where a \tol and dE this would b

@@

\bibliographystyle{mn2e}
\bibliography{references}

>>>>

\begin{abstract}
  Star-forming Compact Dwarf Galaxies (CDGs) resemble the expected
  pristine conditions of the first galaxies in the Universe and
  are the best systems to test models on primordial
galaxy formation and evolution.    
Here we report on one of such CDGs, \tol, which presents
a broad, single peaked, highly symmetric \lya\ line emission that had
evaded theoretical interpretation so far.  
In this paper we explain these features by two different physically
motivated kinematic models: 
an interstellar medium composed by outflowing clumps with 
random motions and an homogeneous gaseous sphere undergoing solid body
rotation.
It is the first time that an observed \lya\ spectrum can be explained
assuming either of these kinematic conditions.
We find that both models independently require high velocities, either
a clump velocity dispersion of \sigmaclump\ with outflows of
\inftyclump\ or a bulk rotation of $348^{+75}_{-48}$ km s$^{-1}$. 
The velocity dispersion in the multiphase model is consistent with a dynamical
mass of $2\times 10^{9}$ M$_{\odot}$, ten times its baryonic mass,
which can be explained if \tol\ is hosted by a dark matter halo of at least
$10^{11}$ M$_{\odot}$; conditions similar to those of Dwarf Elliptical Galaxies.
This work shows the importance of considering multiphase
and rotation kinematics among the possible conditions shaping the
\lya\ spectra.
If future kinematic maps of \tol\ confirm the velocities found by the
multiphase model, it will be the basis to study evolutionary processes that
might be at play during primordial galaxy evolution.
\end{abstract}

@@

With $14$ free parameters our first concern is discovering which are
the most relevant in reproducing \tol's line shape.
The results of the random forest classifier yield that the clump outflow velocity
$v_{\infty,\rm{cl}}$, the clump velocity dispersion $\sigma_{\rm cl}$ and the probability
that the \lya\ emission comes from the clumps $P_{\rm cl}$, are the
most influential parameters in finding a model with low
$\chi^2/d.o.f.$.

Figure \ref{fig:tree} shows as an illustration the results for a
classification tree.  
The tree starts with $28$ and $1962$ models in the low and high
$\chi^2/d.o.f.$ classes, respectively. 
We find that the best classification
yields $13$ and $44$ models in the low and high $\chi^2\d.o.f.$
classes, respectively, after selecting for $v_{\infty,{\rm cl}}<157.0$ \kms,
$\sigma_{{\rm cl}}>55.6$ \kms and $P_{\rm cl}>0.683$. 
The split in two classes is not perfect. 
This means that the 3 parameters in the
model are the most influential, but that some combinations of the
other 11 parameters are also relevant to find a good fit.

From the K-S tests we confirm that the same 3 parameters are the
only ones that can be constrained by observations;
$v_{\infty,\rm{cl}}$ (p-value  $10^{-18}$), $\sigma_{\rm cl}$ (p-value
$10^{-4}$) $P_{\rm cl}$ (p-value $10^{-4}$).
Once again, this test does not mean the other parameters do not
influence the resulting spectra at all; it means that they cannot be
constrained from \tol's observations.

@@

@@

As a test, we run a small set of 100 additional radiative transfer simulations
with random values for all parameters, except for $\sigma_{\rm cl}$,
$v_{\infty {\rm cl}}$, $P_{\rm cl}$ which are within the derived
constraints.
Consistent with the results from the random forest algorithm,
illustrated by the classification tree of Figure \ref{fig:tree}, we
find that $30$ models show $\chi^2/d.o.f.<35$.

Having constrained only 3 parameters, one migh wonder why the other 11
parameters do not seem to matter. 
However, this view is misleading. 
Even if for clumply models the line profile is most sensitive to only
a few parameters \citep{Gronke2016}, there are the rest of parameters
which affect the line profile at a level that cannot be neglected,
i.e. we cannot randomly pick 11 random, reasonable values for these
parameters, and expect to fit the line profile while only varying the
other 3, as the results for the classification tree example show in
Figure \ref{fig:tree}.

@@

\tol\ shows one of the most atypical \lya\ spectra observed so far.
Its flux at the line's center is high compared to other LAEs at low
redshift and the broad, highly symmetrical peak is virtually absent from other
LAEs at low and high redshift
\citep{2012ApJ...751...29Y,LARS,Erb14,Trainor16}. 
Simple shell models
fail to reproduce such a spectrum as reported by \cite{2015A&A...578A...7V}.  
In the previous sections we show how these characteristics can be
explained by two different kinematic models: multiphase ISM and solid
body rotation.

Which model has more
chances to be correct?  
We discard the rotation model by considering that the rotational
velocity of $\sim350$ \kms\ is too high for such a low
mass system. 
\tol's infered rotational velocity is larger than the
Milky Way's ($\sim200$\kms) while its baryonic mass is one order
of magnitude smaller. 
Furthermore, \tol's structural properties seem to be similar to known dwarf
elliptical galaxies. 
The sample of 7 dwarf ellipticals (dE) observed by
\cite{2003AJ....126.1794G} show similar properties as \tol. 
For instance, the dE galaxies IC 3344 and IC 794 have similar absolute $M_V$
magnitudes (-17.10 and -17.19) and sizes (0.90 kpc and 0.82 kpc) as
\tol. 
These dE galaxies have velocity dispersions of $31.1$ \kms and
$44.6$ \kms, respectively,  and their rotational velocities are lower
than $1$ \kms.  
This leads us to prefer the multiphase model as it provides at least
some consistency with kinematic properties of dE galaxies.

Following the results of \cite{2011ApJ...726..108T}, who made a
detailed analysis for all kind of elliptical galaxies including, we
estimate a value for the dynamical mass using the constraints for
thevelocity dispersion $\sigma$  in a spherical system localized in a
region of size $r$

\begin{equation}
M_{\rm dyn} = 3 \frac{\sigma ^{2}r}{G} = 3.48\times10^{9}
\left(\frac{\sigma}{100\ \mathrm{km\ s}^{-1}}\right)^2\left(\frac{r}{\mathrm{kpc}}\right)
M_{\odot}, 
\end{equation}
%
Assuming that the \lya\ emission is entirely powered by star formation 
we use the 3D half-light radius $r_s=2.25$ kpc as the typical size
for the HI region, in the multiphase model the clump velocity dispersion
$\sigma_{\rm{cl}}=$\sigmaclump corresponds to a dynamical mass of
$M_{\rm dyn}=2.31\pm0.04 \times 10^{9}$ $M_{\odot}$, which is ten
times the estimated baryonic mass in \tol.

\cite{2011ApJ...726..108T} showed that  that such dynamical
mass can be explained if a dwarf galaxy is hosted by a dark matter halo of at
least $10^{11}$ M$_{\odot}$ in mass. 
This estimate is based on computing the integrated mass profile of a
spherical dark matter halo with a Navarro-Frenk-White profile with its
concentration following the \emph{median} mass-concentration
relationship found in the Bolshoi simulation
\citep{2012MNRAS.423.3018P}.

These results would imply that \tol\ is part of the dE
class. 
However, there are two puzzles that are opened up by this hypothesis. 
First, dwarf ellipticals are found either in clusters or groups of
galaxies; while \tol\ does not belong either to a group or a cluster
\citep{2001AJ....121..169F,}. 
The second problem is that, unlike dE, \tol\ hosts a bright and compact
startburst; imaging and spectroscopy studies suggest that the
startburst started less than 4 Myr ago, while the low surface
brightness regins are consistent with an age below one Gyr
\citep{2001AJ....121..169F}.

@@

It is the first time that an observed \lya\ profile can be fully
reproduced by either of these two kinematic conditions.
We give preference to the multiphase model as it produces kinematic
conditions that are similar to those in dwarf ellipticals, while the
rotational model produces rotational velocities to high for a dwarf
galaxy.

However, \tol's environment and star forming activity are radically
different from dwarf ellipticals.
We suggest that additional integral field unit observations are the
only way to be certain about the detailed kinematic structure in \tol.

@@

We acknowledge that a final confirmation of our kinematic findings has
to be provided by new observational tests with integral field unit
spectroscopy. 
If our results are confirmed, this would open up a new line of more detailed
enquiries to understand how a compact dwarf galaxy can have the
structural characteristics similar to a dwarf elliptical while being
at the same time isolated and sustaining large starburst.
Such and investigation could provide an evolutionary between star forming
and quiescent stages of dwarf galaxy evolution.

@@

\bibliographystyle{mn2e}
%\bibliography{references}
\begin{thebibliography}{}

\bibitem[\protect\citeauthoryear{{Bacon} et~al.,}{{Bacon}
  et~al.}{2014}]{2014Msngr.157...13B}
{Bacon} R.  et~al., 2014, The Messenger, 157, 13

\bibitem[\protect\citeauthoryear{{Begum}, {Chengalur} \&
  {Karachentsev}}{{Begum} et~al.}{2005}]{2005A&A...433L...1B}
{Begum} A.,  {Chengalur} J.~N.,    {Karachentsev} I.~D.,  2005, \aap, 433, L1

\bibitem[\protect\citeauthoryear{{Dey}, {Spinrad}, {Stern}, {Graham} \&
  {Chaffee}}{{Dey} et~al.}{1998}]{1998ApJ...498L..93D}
{Dey} A.,  {Spinrad} H.,  {Stern} D.,  {Graham} J.~R.,    {Chaffee} F.~H.,
  1998, \apjl, 498, L93

\bibitem[\protect\citeauthoryear{{Dijkstra}}{{Dijkstra}}{2014}]{2014PASA...31...40D}
{Dijkstra} M.,  2014, \pasa, 31, e040

\bibitem[\protect\citeauthoryear{{Dijkstra} \& {Kramer}}{{Dijkstra} \&
  {Kramer}}{2012}]{2012MNRAS.424.1672D}
{Dijkstra} M.,  {Kramer} R.,  2012, \mnras, 424, 1672

\bibitem[\protect\citeauthoryear{{Dijkstra}, {Lidz} \& {Wyithe}}{{Dijkstra}
  et~al.}{2007}]{2007MNRAS.377.1175D}
{Dijkstra} M.,  {Lidz} A.,    {Wyithe} J.~S.~B.,  2007, \mnras, 377, 1175

\bibitem[\protect\citeauthoryear{{Engelbracht}, {Rieke}, {Gordon}, {Smith},
  {Werner}, {Moustakas}, {Willmer} \& {Vanzi}}{{Engelbracht}
  et~al.}{2008}]{2008ApJ...678..804E}
{Engelbracht} C.~W.,  {Rieke} G.~H.,  {Gordon} K.~D.,  {Smith} J.-D.~T.,
  {Werner} M.~W.,  {Moustakas} J.,  {Willmer} C.~N.~A.,    {Vanzi} L.,  2008,
  \apj, 678, 804

\bibitem[\protect\citeauthoryear{{Erb} et~al.,}{{Erb} et~al.}{2014}]{Erb14}
{Erb} D.~K.  et~al., 2014, \apj, 795, 33

\bibitem[\protect\citeauthoryear{{Eskew}, {Zaritsky} \& {Meidt}}{{Eskew}
  et~al.}{2012}]{2012AJ....143..139E}
{Eskew} M.,  {Zaritsky} D.,    {Meidt} S.,  2012, \aj, 143, 139

\bibitem[\protect\citeauthoryear{{Foreman-Mackey}, {Hogg}, {Lang} \&
  {Goodman}}{{Foreman-Mackey} et~al.}{2013}]{2013PASP..125..306F}
{Foreman-Mackey} D.,  {Hogg} D.~W.,  {Lang} D.,    {Goodman} J.,  2013, \pasp,
  125, 306

\bibitem[\protect\citeauthoryear{{Forero-Romero}, {Yepes}, {Gottl{\"o}ber},
  {Knollmann}, {Cuesta} \& {Prada}}{{Forero-Romero} et~al.}{2011}]{CLARA}
{Forero-Romero} J.~E.,  {Yepes} G.,  {Gottl{\"o}ber} S.,  {Knollmann} S.~R.,
  {Cuesta} A.~J.,    {Prada} F.,  2011, \mnras, 415, 3666

\bibitem[\protect\citeauthoryear{{Fricke}, {Izotov}, {Papaderos}, {Guseva} \&
  {Thuan}}{{Fricke} et~al.}{2001}]{2001AJ....121..169F}
{Fricke} K.~J.,  {Izotov} Y.~I.,  {Papaderos} P.,  {Guseva} N.~G.,    {Thuan}
  T.~X.,  2001, \aj, 121, 169

\bibitem[\protect\citeauthoryear{{Garavito-Camargo}, {Forero-Romero} \&
  {Dijkstra}}{{Garavito-Camargo} et~al.}{2014}]{GaravitoCamargo2014}
{Garavito-Camargo} J.~N.,  {Forero-Romero} J.~E.,    {Dijkstra} M.,  2014,
  \apj, 795, 120

\bibitem[\protect\citeauthoryear{{Gavil{\'a}n}, {Ascasibar}, {Moll{\'a}} \&
  {D{\'{\i}}az}}{{Gavil{\'a}n} et~al.}{2013}]{2013MNRAS.434.2491G}
{Gavil{\'a}n} M.,  {Ascasibar} Y.,  {Moll{\'a}} M.,    {D{\'{\i}}az} {\'A}.~I.,
   2013, \mnras, 434, 2491

\bibitem[\protect\citeauthoryear{{Gawiser} et~al.,}{{Gawiser}
  et~al.}{2007}]{2007ApJ...671..278G}
{Gawiser} E.  et~al., 2007, \apj, 671, 278

\bibitem[\protect\citeauthoryear{{Geha}, {Guhathakurta} \& {van der
  Marel}}{{Geha} et~al.}{2003}]{2003AJ....126.1794G}
{Geha} M.,  {Guhathakurta} P.,    {van der Marel} R.~P.,  2003, \aj, 126, 1794

\bibitem[\protect\citeauthoryear{Goodman \& Weare}{Goodman \&
  Weare}{2010}]{goodman2010ensemble}
Goodman J.,  Weare J.,  2010, Communications in applied mathematics and
  computational science, 5, 65

\bibitem[\protect\citeauthoryear{{Greig}, {Komatsu} \& {Wyithe}}{{Greig}
  et~al.}{2013}]{2013MNRAS.431.1777G}
{Greig} B.,  {Komatsu} E.,    {Wyithe} J.~S.~B.,  2013, \mnras, 431, 1777

\bibitem[\protect\citeauthoryear{{Gronke}, {Bull} \& {Dijkstra}}{{Gronke}
  et~al.}{2015}]{2015ApJ...812..123G}
{Gronke} M.,  {Bull} P.,    {Dijkstra} M.,  2015, \apj, 812, 123

\bibitem[\protect\citeauthoryear{{Gronke} \& {Dijkstra}}{{Gronke} \&
  {Dijkstra}}{2016}]{Gronke2016}
{Gronke} M.,  {Dijkstra} M.,  2016, \apj, 826, 14

\bibitem[\protect\citeauthoryear{{Hansen} \& {Oh}}{{Hansen} \&
  {Oh}}{2006}]{Hansen06}
{Hansen} M.,  {Oh} S.~P.,  2006, \mnras, 367, 979

\bibitem[\protect\citeauthoryear{{Harrington}}{{Harrington}}{1973}]{Harrington73}
{Harrington} J.~P.,  1973, \mnras, 162, 43

\bibitem[\protect\citeauthoryear{{Hayashino} et~al.,}{{Hayashino}
  et~al.}{2004}]{2004AJ....128.2073H}
{Hayashino} T.  et~al., 2004, \aj, 128, 2073

\bibitem[\protect\citeauthoryear{{Hayes}}{{Hayes}}{2015}]{Hayes15}
{Hayes} M.,  2015, \pasa, 32, e027

\bibitem[\protect\citeauthoryear{{Herenz} et~al.,}{{Herenz}
  et~al.}{2016}]{Herenz16}
{Herenz} E.~C.  et~al., 2016, \aap, 587, A78

\bibitem[\protect\citeauthoryear{{Hummer} \& {Storey}}{{Hummer} \&
  {Storey}}{1987}]{Hummer1987}
{Hummer} D.~G.,  {Storey} P.~J.,  1987, \mnras, 224, 801

\bibitem[\protect\citeauthoryear{{Izotov}, {Papaderos}, {Guseva}, {Fricke} \&
  {Thuan}}{{Izotov} et~al.}{2004}]{Izotov04}
{Izotov} Y.~I.,  {Papaderos} P.,  {Guseva} N.~G.,  {Fricke} K.~J.,    {Thuan}
  T.~X.,  2004, \aap, 421, 539

\bibitem[\protect\citeauthoryear{{Kennicutt}
  Jr.}{{Kennicutt}}{1998}]{Kennicutt98}
{Kennicutt} Jr. R.~C.,  1998, \araa, 36, 189

\bibitem[\protect\citeauthoryear{{Kova{\v c}}, {Somerville}, {Rhoads},
  {Malhotra} \& {Wang}}{{Kova{\v c}} et~al.}{2007}]{2007ApJ...668...15K}
{Kova{\v c}} K.,  {Somerville} R.~S.,  {Rhoads} J.~E.,  {Malhotra} S.,
  {Wang} J.,  2007, \apj, 668, 15

\bibitem[\protect\citeauthoryear{{Laursen}, {Duval} \& {{\"O}stlin}}{{Laursen}
  et~al.}{2013}]{Laursen2013ApJ...766..124L}
{Laursen} P.,  {Duval} F.,    {{\"O}stlin} G.,  2013, \apj, 766, 124

\bibitem[\protect\citeauthoryear{{Loeb} \& {Rybicki}}{{Loeb} \&
  {Rybicki}}{1999}]{LoebRybicki}
{Loeb} A.,  {Rybicki} G.~B.,  1999, \apj, 524, 527

\bibitem[\protect\citeauthoryear{{Martin}}{{Martin}}{1998}]{1998ApJ...506..222M}
{Martin} C.~L.,  1998, \apj, 506, 222

\bibitem[\protect\citeauthoryear{{Mas-Hesse}, {Kunth}, {Tenorio-Tagle},
  {Leitherer}, {Terlevich} \& {Terlevich}}{{Mas-Hesse}
  et~al.}{2003}]{mashesse03}
{Mas-Hesse} J.~M.,  {Kunth} D.,  {Tenorio-Tagle} G.,  {Leitherer} C.,
  {Terlevich} R.~J.,    {Terlevich} E.,  2003, \apj, 598, 858

\bibitem[\protect\citeauthoryear{{Mej{\'{\i}}a-Restrepo} \&
  {Forero-Romero}}{{Mej{\'{\i}}a-Restrepo} \&
  {Forero-Romero}}{2016}]{2016ApJ...828....5M}
{Mej{\'{\i}}a-Restrepo} J.~E.,  {Forero-Romero} J.~E.,  2016, \apj, 828, 5

\bibitem[\protect\citeauthoryear{{Neufeld}}{{Neufeld}}{1991}]{1991ApJ...370L..85N}
{Neufeld} D.~A.,  1991, \apjl, 370, L85

\bibitem[\protect\citeauthoryear{{Noeske}, {Papaderos}, {Cair{\'o}s} \&
  {Fricke}}{{Noeske} et~al.}{2003}]{2003A&A...410..481N}
{Noeske} K.~G.,  {Papaderos} P.,  {Cair{\'o}s} L.~M.,    {Fricke} K.~J.,  2003,
  \aap, 410, 481

\bibitem[\protect\citeauthoryear{{Orsi}, {Lacey} \& {Baugh}}{{Orsi}
  et~al.}{2012}]{Orsi12}
{Orsi} A.,  {Lacey} C.~G.,    {Baugh} C.~M.,  2012, \mnras, 425, 87

\bibitem[\protect\citeauthoryear{{Orsi}, {Lacey}, {Baugh} \& {Infante}}{{Orsi}
  et~al.}{2008}]{2008MNRAS.391.1589O}
{Orsi} A.,  {Lacey} C.~G.,  {Baugh} C.~M.,    {Infante} L.,  2008, \mnras, 391,
  1589

\bibitem[\protect\citeauthoryear{{{\"O}stlin} et~al.,}{{{\"O}stlin}
  et~al.}{2014}]{LARS}
{{\"O}stlin} G.  et~al., 2014, \apj, 797, 11

\bibitem[\protect\citeauthoryear{{Ott}, {Walter} \& {Brinks}}{{Ott}
  et~al.}{2005}]{2005MNRAS.358.1453O}
{Ott} J.,  {Walter} F.,    {Brinks} E.,  2005, \mnras, 358, 1453

\bibitem[\protect\citeauthoryear{{Padilla}, {Christlein}, {Gawiser},
  {Gonz{\'a}lez}, {Guaita} \& {Infante}}{{Padilla}
  et~al.}{2010}]{2010MNRAS.409..184P}
{Padilla} N.~D.,  {Christlein} D.,  {Gawiser} E.,  {Gonz{\'a}lez} R.~E.,
  {Guaita} L.,    {Infante} L.,  2010, \mnras, 409, 184

\bibitem[\protect\citeauthoryear{{Partridge} \& {Peebles}}{{Partridge} \&
  {Peebles}}{1967}]{PartridgePeebles}
{Partridge} R.~B.,  {Peebles} P.~J.~E.,  1967, \apj, 147, 868

\bibitem[\protect\citeauthoryear{{Prada}, {Klypin}, {Cuesta}, {Betancort-Rijo}
  \& {Primack}}{{Prada} et~al.}{2012}]{2012MNRAS.423.3018P}
{Prada} F.,  {Klypin} A.~A.,  {Cuesta} A.~J.,  {Betancort-Rijo} J.~E.,
  {Primack} J.,  2012, \mnras, 423, 3018

\bibitem[\protect\citeauthoryear{{Pustilnik} \& {Martin}}{{Pustilnik} \&
  {Martin}}{2007}]{pustilnikmartin07}
{Pustilnik} S.~A.,  {Martin} J.-M.,  2007, \aap, 464, 859

\bibitem[\protect\citeauthoryear{{Rivera-Thorsen} et~al.,}{{Rivera-Thorsen}
  et~al.}{2015}]{2015ApJ...805...14R}
{Rivera-Thorsen} T.~E.  et~al., 2015, \apj, 805, 14

\bibitem[\protect\citeauthoryear{{Roth} et~al.,}{{Roth} et~al.}{2005}]{PMAS}
{Roth} M.~M.  et~al., 2005, \pasp, 117, 620

\bibitem[\protect\citeauthoryear{{Steidel}, {Erb}, {Shapley}, {Pettini},
  {Reddy}, {Bogosavljevi{\'c}}, {Rudie} \& {Rakic}}{{Steidel}
  et~al.}{2010}]{2010ApJ...717..289S}
{Steidel} C.~C.,  {Erb} D.~K.,  {Shapley} A.~E.,  {Pettini} M.,  {Reddy} N.,
  {Bogosavljevi{\'c}} M.,  {Rudie} G.~C.,    {Rakic} O.,  2010, \apj, 717, 289

\bibitem[\protect\citeauthoryear{{Swaters}, {Sancisi}, {van Albada} \& {van der
  Hulst}}{{Swaters} et~al.}{2009}]{2009A&A...493..871S}
{Swaters} R.~A.,  {Sancisi} R.,  {van Albada} T.~S.,    {van der Hulst} J.~M.,
  2009, \aap, 493, 871

\bibitem[\protect\citeauthoryear{{Tasitsiomi}}{{Tasitsiomi}}{2006}]{2006ApJ...645..792T}
{Tasitsiomi} A.,  2006, \apj, 645, 792

\bibitem[\protect\citeauthoryear{{Tassis}, {Kravtsov} \& {Gnedin}}{{Tassis}
  et~al.}{2008}]{2008ApJ...672..888T}
{Tassis} K.,  {Kravtsov} A.~V.,    {Gnedin} N.~Y.,  2008, \apj, 672, 888

\bibitem[\protect\citeauthoryear{{Thuan} \& {Izotov}}{{Thuan} \&
  {Izotov}}{1997}]{Thuan97}
{Thuan} T.~X.,  {Izotov} Y.~I.,  1997, \apj, 489, 623

\bibitem[\protect\citeauthoryear{{Tollerud}, {Bullock}, {Graves} \&
  {Wolf}}{{Tollerud} et~al.}{2011}]{2011ApJ...726..108T}
{Tollerud} E.~J.,  {Bullock} J.~S.,  {Graves} G.~J.,    {Wolf} J.,  2011, \apj,
  726, 108

\bibitem[\protect\citeauthoryear{{Trainor}, {Strom}, {Steidel} \&
  {Rudie}}{{Trainor} et~al.}{2016}]{Trainor16}
{Trainor} R.~F.,  {Strom} A.~L.,  {Steidel} C.~C.,    {Rudie} G.~C.,  2016,
  \apj, 832, 171

\bibitem[\protect\citeauthoryear{{Verhamme}, {Orlitov{\'a}}, {Schaerer} \&
  {Hayes}}{{Verhamme} et~al.}{2015}]{2015A&A...578A...7V}
{Verhamme} A.,  {Orlitov{\'a}} I.,  {Schaerer} D.,    {Hayes} M.,  2015, \aap,
  578, A7

\bibitem[\protect\citeauthoryear{{Verhamme}, {Schaerer} \&
  {Maselli}}{{Verhamme} et~al.}{2006}]{2006A&A...460..397V}
{Verhamme} A.,  {Schaerer} D.,    {Maselli} A.,  2006, \aap, 460, 397

\bibitem[\protect\citeauthoryear{{Yamada}, {Matsuda}, {Kousai}, {Hayashino},
  {Morimoto} \& {Umemura}}{{Yamada} et~al.}{2012}]{2012ApJ...751...29Y}
{Yamada} T.,  {Matsuda} Y.,  {Kousai} K.,  {Hayashino} T.,  {Morimoto} N.,
  {Umemura} M.,  2012, \apj, 751, 29

\end{thebibliography}
